\documentclass[../index.tex]{subfiles}
\begin{document}

\part{The Dream}

\chapter{Why reinventing the wheel?}
The first flaw of creating ist own game engie is that the wheel is reinvented.
But why to choose against the general saying that one should not try to recreated something that already exists?
Well, here are some reasons why:


\begin{itemize}

\item In a world where every year a new "standard" appears for fundamental software technology I simply do not care any more. Why should I not be allowed to do what the market leaders do all the time?

\item It is educational and fun thinking and creating a complex framework like a gaming engine.

\item Independence. Not one industry arse can ever do anything about my engine and let me pay in the end, like it happened for Unity recently.

\item Opportunity of having full control. But that is just an excuse.

\end{itemize}


\chapter{Choosing technology}
Choosing technology was based on personal preference and availability.


\begin{worddefs}

\item[Java.]Although there are other more efficient languages around, like C++ or C\#, I chose Java just because these projects are easier to transfer into my work environment and back with eclipse (We use Java and Eclipse at work).

\item[Ivy.] I deliberately went against Maven because I just do not understand in detail how it works. And after days if not even weeks of troubleshooting problems I would not even have if I don't use Maven I just got rid of it. But Ivy and dependency gathering of Java libraries seemed fine enough.

\item[JOGL.] Why not LWJGL? Because i started with JOGL, and JOGL provides a nice Top Level Interface for creating Windows etc. (NEWT). LWJGL seemed more complex in that regard. Also, JOGL is much much smaller libarary wise.

\item[JOAL.] The Nearness to JOGL makes it obvious.

\item[Blender.] Because it is a good 3D allrounder and free.

\item[GIMP.] The same in 2D pixel graphics.

\item[Inkscape.] The same in 2D vector graphics.

\item[Github.] Because i need a good exchange platform for transproting code between home and work, and also provides version control on the fly.

\item[LaxTex.] Because i wanted to learn it, and also because it is freely available and has a lot of approved technology.

\end{worddefs}


\end{document}
